The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)

### 2016-06-10 WSSSPE4_proposal/WSSSPE4_proposal.tex
fixed Neimeyer -> Niemeyer
fixing budget

\item {\bf Participant Support: } \$40,000
{\it Funds are requested to support travel for 18 participants and 2 presenters from US institutions across the country to travel to New Orleans. Estimated costs include airfare, 2 nights hotel and workshop fees.}

\item {\bf Other Direct Costs: } No funds requested. 
\item {\bf Indirect Costs: } \$1,755

@@

\item {\bf Total Costs: } \$24,755

>>>>

\item {\bf Participant Support: } \$41,500
{\it Funds are requested to partially support travel for 25 participants and presenters (at \$1,500 per participant) from US institutions across the country from the US to Manchester, UK, and 3 participants/presenters (at \$1,000 each)  from US institutions who are already in Europe to travel to Manchester, and 2 participants/presenters  (at \$500 each)  from US institutions who are already in the UK to travel to Manchester. Reimbursable costs include airfare, hotel, and sustenance.}

\item {\bf Other Direct Costs: } No funds requested. 
\item {\bf Indirect Costs: } \$1,524

@@

\item {\bf Total Costs: } \$49,024
